 

### 2021-01-27 vertical-thermal-review.Rmd
review of leaf temperature section

## Leaf temperature and hydraulics

@@

In addition, leaf size impacts leaf temperature. While small leaves remain within a few degrees of $T_{air}$, regardless of stomatal conductance, wider leaves can have temperatures deviating more from air temperature [@fauset_differences_2018]. Large leaves (with greater leaf width) can be significantly cooler than $T_{air}$ under low radiation with stomata open [@leighInfluenceLeafSize2017], and significantly hotter under high radiation with stomata closed.

@@

**Aligning with biophysical expectations, field observations have shown that leaf temperatures are influenced by the biophysical environment and leaf traits.**
1.	Air T
2.	Solar radiation
3.	Leaf traits

>>>>

## Leaf temperature

### Biophysical drivers

@@

In addition, leaf size, which itself varies with height (Table `r table_leaf_traits`), impacts leaf temperature. While small leaves remain within a few degrees of $T_{air}$, regardless of stomatal conductance, wider leaves can have temperatures deviating more from air temperature [@fauset_differences_2018]. Large leaves (with greater leaf width) can be significantly cooler than $T_{air}$ under low radiation with stomata open [@leighInfluenceLeafSize2017], and significantly hotter under high radiation with stomata closed.

@@

### In-situ observations
**Vertical profiles in microclimate (Fig. `r fig_NEON_vertical`) and leaf traits (Table `r table_leaf_traits`) together shape in-situ leaf temperatures according to the principles outlined above.** 
The net effect....
